Network Configuration Synthesis with Abstract Topologies

### 2016-11-04 paper/abstraction/paper.tex
updates

\newcommand{\inference}[4]{
    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
    \node at (#1 + .34, .6) {$e_1$};
    \node at (#1 + .34, 1.9) {$e_2$};
    \node at (#1, -.8) {#2};
    \node at (#1, 3.3) {#4};
    \draw [] (#1, 2.5) circle [radius=0.45] node {$n$};
    \draw [] (#1, 0) circle [radius=0.45] node {$m$};
    \draw [] (#1, .45) -- (#1, 2.05);
}

@@

  \vspace*{1em}
  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  %\vspace{-1em}
\end{figure*}

@@

For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint paths to them from the source and all 8 paths are disjoint.

In order to learn information about disjoint paths between routers, we develop a series of sound inference rules for facts of the above form. Figure~\ref{fig:inference-rules} shows each of the inference rules.

>>>>

\newcommand{\inference}[4]{
    \node[draw, anchor=west] at (#1 + .4, 1.25) {#3};
    \node at (#1 + .34, .6) {$e_1$};
    \node at (#1 + .34, 1.9) {$e_2$};
    \node at (#1, -.8) {#2};
    \node at (#1, 3.3) {#4};
    \draw [] (#1, 2.5) circle [radius=0.45] node {$m$};
    \draw [] (#1, 0) circle [radius=0.45] node {$n$};
    \draw [] (#1, .45) -- (#1, 2.05);
}

@@

  \vspace*{1em}
  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:abstract-analysis}
  %\vspace{-1em}
\end{figure*}

@@

For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint to them from the source and all 8 paths are disjoint.

%suppose we want to compute the number of disjoint paths from the local ToR role $(TL,0,0)$ for
\ryan{TODO: probably need a new image for local prefixes?}
